The Effects of Telluric Lines in Radial Velocity Searches for Planets with Iodine Cells as Calibrators\altaffilmark{1}

### 2016-02-29 telluric/ms.tex
First couple paragraphs for tellurics intro and citations.

\def\beq{\begin{equation}}
\def\eeq{\end{equation}}
\def\bcm{\begin{comment}}
\def\ecm{\end{comment}}
\def\mps{m~s$^{-1}$}
\def\msini{M\sin{i}}
\def\mjup{M_{\rm Jup}}
\def\msol{M_{\odot}}

@@

\title
{
The Effects of Telluric Lines in Radial Velocity Searches for Planets with Iodine
Cell as Calibrators\altaffilmark{1}
}

@@

The radial velocity method has contributed to hundreds of planetary
discoveries and Kepler follow-ups. The current precision is at 1--2
m/s, with limiting factor being stellar activity and RV systematics,
instrumental or software.

>>>>

\def\beq{\begin{equation}}
\def\eeq{\end{equation}}
\def\bcm{\begin{comment}}
\def\ecm{\end{comment}}
\def\mps{m~s$^{-1}$}
\def\msini{M\sin{i}}
\def\mjup{M_{\rm Jup}}
\def\msol{M_{\odot}}
\def\kepler{{\it Kepler}}

@@

\title
{
The Effects of Telluric Lines in Radial Velocity Searches for Planets with Iodine
Cells as Calibrators\altaffilmark{1}
}

@@

The first exoplanets around main-sequence stars were discovered by the
radial velocity (RV) method, where precise Doppler spectroscopy
measures the wavelength shift of the host stars induced by the
gravitational pull of the planets \citep{1988ApJ...331..902C,
  1989Natur.339...38L, 1993ApJ...413..339H, 1995Natur.378..355M,
  1996ApJ...464L.153B}. Since then, the RV method has discovered
hundreds of planetary systems (see exoplanets.org; \citealt{eod2014})
and contributed to numerous confirmation and characterization of
exoplanets discovered by the transit method (e.g., for
\kepler\ follow-up observations; \citealt{Marcy2014}).

The current best RV precision is around 1~m/s, attainable via two
wavelength calibration methods: ThAr lamp emission line calibration
(e.g., ELODIE and HARPS; \citealt{elodie, harps-s}) and iodine cell
absorption line calibration (e.g., Keck/HIRES; \citealt{butler1996}).
